P01 & root+flags & ctrl & \fpath{config} & \fpath{config} & \fpath{config/db.env} \tabularnewline
P02 & root+flags & ctrl & \fpath{ops} & \fpath{ops} & \fpath{ops/runtime.env} \tabularnewline
P03 & sib. pivot & ctrl & \fpath{config} & \fpath{config} & \fpath{config/feature_flags.yml} \tabularnewline
P04 & sib. pivot & ctrl & \fpath{config} & \fpath{config} & \fpath{config/service.yml} \tabularnewline
P05 & root+flags & pyaml & \fpath{README.md} & \fpath{README.md} & \fpath{README.md} \tabularnewline
P06 & sib. pivot & pyaml & \fpath{README.md} & \fpath{README.md} & \fpath{README.md} \tabularnewline
P07 & root+flags & envns & \fpath{README.md} & \fpath{README.md} & \fpath{README.md} \tabularnewline
P08 & sib. pivot & envns & \fpath{README.md} & \fpath{README.md} & \fpath{README.md} \tabularnewline
P09 & root+flags & decpl & \fpath{README.rst} & \fpath{README.rst} & \fpath{README.rst} \tabularnewline
P10 & sib. pivot & decpl & \fpath{README.rst} & \fpath{README.rst} & \fpath{README.rst} \tabularnewline
P11 & parent esc. & ctrl & \fpath{config} & \fpath{config} & \fpath{config/db.env} \tabularnewline
P12 & parent esc. & ctrl & \fpath{ops} & \fpath{ops} & \fpath{ops/runtime.env} \tabularnewline
P13 & parent esc. & ctrl & \fpath{config} & \fpath{config} & \fpath{config/feature_flags.yml} \tabularnewline
P14 & parent esc. & ctrl & \fpath{config} & \fpath{config} & \fpath{config/service.yml} \tabularnewline
P15 & parent esc. & pyaml & \fpath{README.md} & \fpath{README.md} & \fpath{README.md} \tabularnewline
P16 & parent esc. & pyaml & \fpath{README.md} & \fpath{README.md} & \fpath{README.md} \tabularnewline
P17 & parent esc. & envns & \fpath{README.md} & \fpath{README.md} & \fpath{README.md} \tabularnewline
P18 & parent esc. & envns & \fpath{README.md} & \fpath{README.md} & \fpath{README.md} \tabularnewline
P19 & parent esc. & decpl & \fpath{README.rst} & \fpath{README.rst} & \fpath{README.rst} \tabularnewline
P20 & parent esc. & decpl & \fpath{README.rst} & \fpath{README.rst} & \fpath{README.rst} \tabularnewline
P21 & root+flags & dynac & \fpath{docs/secrets.md} & \fpath{docs/secrets.md} & \fpath{docs/secrets.md} \tabularnewline
P22 & sib. pivot & dynac & \fpath{docs/validation.md} & \fpath{docs/validation.md} & \fpath{docs/validation.md} \tabularnewline
P23 & root+flags & pydst & \fpath{docs/index.md} & \fpath{docs/index.md} & \fpath{docs/index.md} \tabularnewline
P24 & sib. pivot & pydst & \fpath{docs/index.md} & \fpath{docs/index.md} & \fpath{docs/index.md} \tabularnewline
P25 & root+flags & djcfg & \fpath{docs/values.rst} & \fpath{docs/values.rst} & \fpath{docs/values.rst} \tabularnewline
P26 & sib. pivot & djcfg & \fpath{docs/values.rst} & \fpath{docs/values.rst} & \fpath{docs/values.rst} \tabularnewline
P27 & root+flags & pydot & \fpath{README.md} & \fpath{README.md} & \fpath{README.md} \tabularnewline
P28 & sib. pivot & pydot & \fpath{README.md} & \fpath{README.md} & \fpath{README.md} \tabularnewline
P29 & root+flags & cfgap & \fpath{README.md} & \fpath{README.md} & \fpath{README.md} \tabularnewline
P30 & sib. pivot & cfgap & \fpath{README.md} & \fpath{README.md} & \fpath{README.md} \tabularnewline
P31 & parent esc. & dynac & \fpath{docs/secrets.md} & \fpath{docs/secrets.md} & \fpath{docs/secrets.md} \tabularnewline
P32 & parent esc. & dynac & \fpath{docs/validation.md} & \fpath{docs/validation.md} & \fpath{docs/validation.md} \tabularnewline
P33 & parent esc. & pydst & \fpath{docs/index.md} & \fpath{docs/index.md} & \fpath{docs/index.md} \tabularnewline
P34 & parent esc. & pydst & \fpath{docs/index.md} & \fpath{docs/index.md} & \fpath{docs/index.md} \tabularnewline
P35 & parent esc. & djcfg & \fpath{docs/values.rst} & \fpath{docs/values.rst} & \fpath{docs/values.rst} \tabularnewline
P36 & parent esc. & djcfg & \fpath{docs/values.rst} & \fpath{docs/values.rst} & \fpath{docs/values.rst} \tabularnewline
P37 & parent esc. & pydot & \fpath{README.md} & \fpath{README.md} & \fpath{README.md} \tabularnewline
P38 & parent esc. & pydot & \fpath{README.md} & \fpath{README.md} & \fpath{README.md} \tabularnewline
P39 & parent esc. & cfgap & \fpath{README.md} & \fpath{README.md} & \fpath{README.md} \tabularnewline
P40 & parent esc. & cfgap & \fpath{README.md} & \fpath{README.md} & \fpath{README.md} \tabularnewline
\bottomrule
